%LaTeX document written by Max Stillwell.
\documentclass[12pt]{article}
\usepackage{parskip}
\usepackage[top=1in,right=1in,left=1.5in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=false, pdftoolbar=true, pdfmenubar=true, pdfstartview={FitV}, pdftitle={Max Stillwell CVE Report}, pdfauthor={Max Stillwell}, pdfnewwindow=true, colorlinks=true, linkcolor=blue, citecolor=green, filecolor=magenta, urlcolor=blue}

\title{CVE Usage Report}
\author{Max Stillwell}
\date{\today}

\setlength{\parskip}{0.5cm}
\setlength{\parindent}{1cm}

\begin{document}
 \maketitle

 \noindent Specs: \\
 OS: Windows 7 x64 \\
 Video Card: NVIDIA GeForce GT 230M \\
 Ram: 6.00 GB \\[0.5cm]

 The first thing I'd note about my use of CVE is that even if you get your password wrong it will try to log all the way in. This closes the log in screen forcing you to close CVE and restart  it again to try you password again which can be bothersome when you can't remember what your password was. Also in the confirm registration screen the email field cuts off long emails which  confused me for awhile as I thought I forgot to type some of my email address. Next thing I'll mention is that I get horrible fps (around 9 - 14fps) on Windows 7 with a NVIDIA GeForce GT  230M. Along the line of graphics based things in some spots I get a weird kind of z-clipping, not sure how to explain it and I didn't catch a screenshot when it happened. Another graphics  thing I have is that at one point it couldn't find a file and gave an error in a new window. I went to close that window and the whole program closed. I kinda forgot to get the name of the  file but it was surprising when everything went away. A suggestion for  that chat box I have  is to make it so you can filter out certain things. There was a point when I was talking with  you and moved into a spot that needed rendering and it flooded the chat and  making me miss that  you said something. It'd be nice to have it filter rendering info from chat. 
\end{document} 
​