\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\title{GUS Use Cases}
\date{}
\begin{document}
  \maketitle
  This is an attempt to further define GUS use cases. It is based
  off prototyping that is occuring, as well as planning down the
  road for creating new / using existing systems.
 
\section{System Functions}
 
 \subsection{Submit New User Account}
 Description of the subsection.
 
 
 \textbf{Actors:} New User, Administrator, Server \\

 
 \textbf{Goals:} To add a new user in the GUS environment. \\
 
 
 \textbf{Preconditions:} None. \\
 
 
 \textbf{Summary:} A new user or an administratore navigates to the user
      registration page. Either enters the new user
      information, and then submit the information. The GUS
      environment performs necessary checks, and adds the
      user if they pass the checks. \\
 
 
 \textbf{Related use cases:} New User Information Sent to GUS. \\
 
 
 \textbf{Steps:}
\begin{enumerate}
  \item New user / existing administrator fills out user registration form.
  \item The submit button is pressed.
  \item New User Information is Sent To GUS.
  \begin{enumerate}
   \item If user registration by admin is set, send to pending user db queue.
   \item Otherwise, send to registered users.
  \end{enumerate}
  \item Send user a confirmation on receipt of registration.
\end{enumerate}
   
   
 \textbf{Alternative:} User cancels submission. \\
  
  
 \textbf{Fail:} User is recycled to user page with correct content
      inserted back into form, and an error message is
      displayed to indicated the problem (internal, user
      error). \\


 \subsection{New User Information Sent to GUS}
   Actions for incoming new user data.
 
 \textbf{Actors:} New user / existing administrator,
                  User Registration Page, Server \\

 
 \textbf{Goals:} Evaluate new user information if
                 necessary, cache the information,
                 and then submit the user information
                 to the Server. \\
 
 
 \textbf{Preconditions:} Use case Submit New User Account
                         completed. \\
 
 
 \textbf{Summary:} New user information is recieved, and then
                   cached (in case the database is not reachable).
                   The cache is then submitted to be saved in the
                   database. \\
 
 
 \textbf{Related use cases:} Submit Cache To Server. \\
 
 
 \textbf{Steps:}
\begin{enumerate}
  \item Receive new user data.
  \item Add data to cache data.
  \item Submit Cache To Server.
  \begin{itemize}
   \item If success:
   \begin{enumerate}
    \item Clear the cache.
    \item Go through each account entry, and send notifications to
          new account marked with the notify flag. Then clear flag.
   \end{enumerate}
   \item Else, notify the system administrators of database comm error.
  \end{itemize}
\end{enumerate}
   
   
 \textbf{Alternative:} None. \\
  
  
 \textbf{Fail:} If Submit Cache To Server fails. \\


\end{document}
