\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\title{GUS Major Scrum Meeting}
\date{}
\begin{document}
\textbf{GUS Software Team, Group 5} \\
 
\textbf{Minutes of the meeting of GUS Group 5} \\
Wegner, Leah - Group Leader\\
 
\textbf{BEL 205, UI Campus, Moscow ID 83843} \\
 
\textbf{On October 28th, 2010 13:30} \\
 
\textbf{Present}\\
 Bianchetti, Tim\\
 Blair, Colby\\
 Nilson, Alex\\
 Wegner, Leah\\
 
\textbf{In Attendance}\\
None \\
 
\section{Actions for consideration} \\
 
 \subsection{Action}
  \begin{itemize}
   \item All group members are to decide on items to go into a major backlog that will hold items until semester end
   \item All members will also decide on items derived from backlog for the 2 week Scrum sprintlog
   \item This is the first meeting, so we have no previous minutes. We also did not need to conduct a Scrum Review or Reflection.
   \item Scrum Planning
   \begin{itemize}
    \item Setup CVE.
    \item Start with GUI (visual representation).
    \begin{itemize}
     \item Consider Iffy / ambiguous use cases in relation to the GUI representation.
     \end{itemize}
    \item Create class diagrams.
    \item Create state charts if they are useful at this stage.
    \item Create action charts if they are usefuly as well.
    \item Every member should pick at least one user-clickable use case and refine it in the usecase master file.
    \item base prototyping of those use cases.
   \end{itemize}
  \end{itemize}

\section{Any Other Business}
\begin{itemize}
   \item Division of labor will begin on the next daily scrum meeting, when everyone has a change to look at the use cases they may want to prototype.
   \item The dates for future meetings are 21:00 via Skype.
\end{itemize}
   
\section{New Business}
None\\
   
\textbf{Meeting closed at 13:45} \\
 
Leah Wegner
 
October 28th, 2010
 
\end{document}

