\documentclass[10pt, oneside, letterpaper]{book}
\usepackage{ifpdf}
\usepackage[colorlinks,bookmarksopen]{hyperref}
\begin{document}
\voffset=-1.25in
\pagestyle{empty}
\begin{center}
\textbf{
\paragraph{TEAM ONE: RELIGIOUS AND ETHNIC}
\paragraph{Regular Meeting of Software Developers}
\paragraph{Thursday, November 11, 2010, 1:20 p.m.}
\paragraph{Bauman Engineering Laboratory, Room 205}
\paragraph{ }
}
\end{center}
\begin{enumerate}
\itemindent=-75pt
\rightmargin=0pt
\item{Call to Order---John Sandmeyer, Team Leader}
\item{Members Attending: John Sandmeyer, Brett Hitchcock, Cynthia Rempel, and Abhay Patil.}
\item{Leader's Report: completed writing website, but needs to post in repository.}
\item{Team's Report: completed installing servers on computers for testing dynamic content.}
\item{Mr. Sandmeyer assigned the following roles to members}
\begin{itemize}
\itemindent=-75pt
\item Mr. Sandmeyer will construct database, PDO, and setup Github site
\item Mr. Laurino will construct a personal user control panel
\item Mr. Hitchcock will construct administrative control panel
\item Ms. Rempel will construct an authentication form using PHP mail function to activate the password to be hased using SHA1 and SALT
\item Mr. Patil will construct a registration form with verfication based on regular expressions
\end{itemize}
\item{Team agreed to do between sprint meetings via the "reply all" feature of email, Ms. Rempel agreed to send a group email by the end of the day.}
\item{Mr. Sandmeyer obtained Dr. Jeffery's approval of the plan}
\item{Unfinished business:}
\begin{itemize}
\itemindent=-75pt
\item Mr. Sandmeyer posts his site to the repository
\item team tests their servers configurations using Mr. Sandmeyer's site
\item UML digrams needed for HW6
\item Presentation needed for HW6
\item Written documentation for HW6
\end{itemize}
\item{New business:}
\begin{itemize}
\itemindent=-75pt
\item Team members will complete their assigned tasks
\item Team members will report their progress using "reply all" and making sure the previous emails are at the bottom of their reply
\item UML diagrams, presentation, and written documentation for HW6
\end{itemize}
\item{Date of next meeting: December 2, 2010}
\item{Adjournment}
\end{enumerate}
\end{document}

