\documentclass[12pt, oneside, letterpaper]{article}
\usepackage{ifpdf}
\usepackage[colorlinks,bookmarksopen]{hyperref}
\usepackage{layout}
\usepackage{lscape}
\textwidth=475pt
\textheight=700pt
\hoffset=-.5in
\voffset=-1.25in
\begin{document}
\begin{center}
\textbf{
PHP TEAM \\
Regular Meeting of Software Developers \\
Tuesday, November 16, 2010, 1:20 p.m. \\
Bauman Engineering Laboratory, Room 205 \\
}
\end{center}
\begin{enumerate}
\rightmargin=0pt
\item{Call to Order---John Sandmeyer, Team Leader}
\item{Members Attending: John Sandmeyer, Brett Hitchcock, Cynthia Rempel, Abhay Patil, Chaylo Laurino, Alex Nilson, and Steven Long}
\item{Leader's Report: members had not signed up for github.}
\item{Team's Report: Mr. Hitchcock completed the code for regular expressions verfication, Ms. Rempel completed use case diagrams, and some communication diagrams}
\item{Members attending the meeting signed up for github, and emailed their username to john.l.sandmeyer@gmail.com}
\item{Mr. Sandmeyer assigned the following roles to members}
\begin{itemize}
\item Mr. Sandmeyer will construct database, PDO, grants group access to production server Johnls.net, and setup Github site
\item Mr. Laurino will construct a personal user control panel
\item Mr. Hitchcock will construct administrative control panel
\item Ms. Rempel will construct an authentication form using PHP mail function to activate the password to be hased using SHA1 and SALT
\item Mr. Patil will construct a registration form with verfication based on regular expressions
\item Mr. Nilson will construct a database administration form
\item Mr. Blair will decide whether users a foreign key for groups, or groups are a foriegn key for users
\item Mr. Long will construct interaction diagrams
\end{itemize}
\item{Ms. Rempel agreed to email the group a copy of the minutes}
\item{Unfinished business:}
\begin{itemize}
\item UML diagrams, presentation and written documentation for HW6
\end{itemize}
\item{New and Continuing business:}
\begin{itemize}
\item Team members will complete their assigned tasks
\item UML diagrams, presentation, and written documentation for HW6
\end{itemize}
\item{Date of next meeting: \textbf{4:00 November 29, 2010, via Skype}}
\item{Adjournment}
\end{enumerate}\end{document}
