\documentclass[12pt]{report}
\usepackage{parskip}
\usepackage[top=1in,right=1in,left=1in,bottom=1in]{geometry}
\usepackage{fancyhdr}

\fancyhf{}
\headheight 14.49998pt
\pagestyle{fancy}
\lhead{3/4/11}
\rhead{GusPy Code Inspection Summary}
\cfoot{PAGE}
\rfoot{\thepage}

\setlength{\parskip}{0.25pt}
\setlength{\parindent}{0.0cm}

\begin{document}
 \textbf{Positions:}
  \begin{itemize}
   \item Coordination: Mike
   \item Secretary: Max
   \item Authors:
   \begin{itemize}
    \item Joran - Roles
    \item Mike - Emailer
    \item Sasha - Calendar
   \end{itemize}
   \item Reviewers:
   \begin{itemize}
    \item Jacob
    \item Lee
    \item Nathan
    \item Mike
    \item Sasha
    \item Joran
   \end{itemize}
  \end{itemize}

 \textbf{\\[0.5pt] gus\_roles/models.py}\newline
 \textbf{Talker:} Mike\newline
 Questions/thoughts that came up:
 \begin{itemize}
  \item Mike: Why use `super' in `with\_user\_in\_group'?\newline 
           Joran: Not sure, all examples found were that way.
  \item Dr J: Do lists scale well in Django/Python?\newline
           Mike: Yes, especially as these particular lists will never be unreasonably long.
  \item Possible Code Change on Lines 212-213.
  \item Mike: Why use setUsers, setGroup, setName?\newline
           Joran: Django requires that if you want both getters and setters you need both, makes nicer way to access things.
 \end{itemize}

 \textbf{\\[0.5pt] gus\_emailer/view.py}\newline
 \textbf{Talker:} Sasha \& Joran\newline
 Questions/thoughts that came up:
 \begin{itemize}
  \item Possible Code Change in `check(request)'. Needs an update since users work.
 \end{itemize}

 \textbf{\\[0.5pt] views/gus\_emailer/index.html}\newline
 \textbf{Talker:} Joran\newline
 Questions/thoughts that came up:
 \begin{itemize}
  \item Dr J: What is the base.html look like/do?\newline
           Joran: The template look of the page, sets up a base page to work from.
 \end{itemize}

 \textbf{\\[0.5pt] views/gus\_calendar/month\_view.html}\newline
 \textbf{Talker:} Joran\newline
 Questions/thoughts that came up:
 \begin{itemize}
  \item Dr J: Calendars seem easy and generic, is there a Django one? Was ours made from scratch?\newline
          Sasha: Probably online, but that would not teach us anything, so I wrote it from scratch.
 \end{itemize}
\end{document} 

​
